---
title: "README"
author: "Roberto Preste"
date: "`r Sys.Date()`"
output: 
  github_document: 
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# mitovizR  

Plot variants on the human mitochondrial genome. Currently supports plotting variants contained in VCF files.  

## Overview  

mitovizR is a simple tool to plot human mitochondrial variants on a graphical representation of the human mitochondrial genome. It currently supports plotting variants stored in a VCF file, although other options are being developed (if you want to contribute, you're welcome!).  

## Installation  

mitovizR can be installed from GitHub using `devtools`:  

```{r, eval=FALSE}
devtools::install_github("robertopreste/mitovizR")
```

Official installation from CRAN coming soon!  

## Usage  

In order to plot human mitochondrial variants contained in a VCF file named "HG00119.vcf" and present in the current working directory:  

```{r, eval=FALSE}
mitovizR::plot_vcf("HG00119.vcf")
```


## Help  

If you found a bug, or want to suggest an improvement, please feel free to open an [issue](https://github.com/robertopreste/mitovizR/issues).  

